Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE5.1) \& The State of Sustainable Software -- TITLE NEEDS WORK

### 2018-03-30 WSSSPE5.1_report/WSSSPE5.1_paper.tex
Kill whitespace errors in a separate commit.
I have a rather strict editor setup.
Add Rob's full details.

\author{Daniel~S.~Katz$^{(1)}$,
Caroline $^{(2)}$,
Rob $^{(3)}$,
Alexander $^{(4)}$,
Stephan\ $^{(5)}$\
please add full names, affiliations, orcids
%Kyle~E.~Niemeyer$^{(2)}$,
%Sandra~Gesing$^{(3)}$,
%Lorraine~Hwang$^{(4)}$,
%Wolfgang~Bangerth$^{(5)}$,
%Simon~Hettrick$^{(6)}$,
%Ray Idaszak$^{(7)}$,
%Jean~Salac$^{(8)}$,
%Neil~Chue~Hong$^{(9)}$,
%Santiago~N\'u\~nez-Corrales$^{(10)}$,
%Alice~Allen$^{(11)}$,
%R.~Stuart~Geiger$^{(12)}$,
%Jonah~Miller$^{(13)}$,
%Emily~Chen$^{(14)}$,
%Anshu~Dubey$^{(15)}$,
%Patricia~Lago$^{(16)}$
%\\Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ department/school, city, country; email; ORCID: orcid}
%
\thanks{{}$^{(3)}$ department/school, city, country; email; ORCID: orcid}
%
\thanks{{}$^{(4)}$ department/school, city, country; email; ORCID: orcid}
%
\thanks{{}$^{(5)}$ department/school, city, country; email; ORCID: orcid}
%

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Caroline $^{(2)}$,
Robert~Haines$^{(3)}$,
Alexander $^{(4)}$,
Stephan\ $^{(5)}$\
please add full names, affiliations, orcids
%Kyle~E.~Niemeyer$^{(2)}$,
%Sandra~Gesing$^{(3)}$,
%Lorraine~Hwang$^{(4)}$,
%Wolfgang~Bangerth$^{(5)}$,
%Simon~Hettrick$^{(6)}$,
%Ray Idaszak$^{(7)}$,
%Jean~Salac$^{(8)}$,
%Neil~Chue~Hong$^{(9)}$,
%Santiago~N\'u\~nez-Corrales$^{(10)}$,
%Alice~Allen$^{(11)}$,
%R.~Stuart~Geiger$^{(12)}$,
%Jonah~Miller$^{(13)}$,
%Emily~Chen$^{(14)}$,
%Anshu~Dubey$^{(15)}$,
%Patricia~Lago$^{(16)}$
%\\Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ department/school, city, country; email; ORCID: orcid}
%
\thanks{{}$^{(3)}$ University of Manchester, Manchester, UK; robert.haines@manchester.ac.uk; ORCID: 0000-0002-9538-7919}
%
\thanks{{}$^{(4)}$ department/school, city, country; email; ORCID: orcid}
%
\thanks{{}$^{(5)}$ department/school, city, country; email; ORCID: orcid}
%
